### 2022-10-07 doc/manuscript/translocation.qmd
Add text to frame introduction

---
format: docx
editor: visual
csl: science.csl
bibliography: translocation.bib
reference-doc: translocation.docx
---

@@

>>>>

---
format: docx
editor: visual
csl: science.csl
bibliography: translocation.bib
reference-doc: translocation_style_ref.docx
---

@@

Severe effects of disease on global biodiversity (bats, primates, amphibians, corals, etc.)

Host evolution and population persistence/recovery

-   Tasmanian devils: Epstein et al. (2016)

-   Frogs in Australia: Grogan et al. (2018), McKnight et al. (2020)

-   Frogs in Panama: Voyles et al. (2018)

-   Frogs in the Sierra Nevada: Knapp et al. (2016)

Population reestablishment using reintroduction of resistant hosts

-   Mendelson et al. (2019)

-   Scheele et al. (2021)

-   Joseph and Knapp (2018)
